An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2021-09-27 gas-adsorption/gas-ads-revtex.tex
convert paper to revtex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%This is the LaTeX ARTICLE template for RSC journals
%Copyright The Royal Society of Chemistry 2016
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[twoside,twocolumn,9pt]{article}
\usepackage{extsizes}
\usepackage[super,sort&compress,comma]{natbib} 
\usepackage[version=3]{mhchem}
\usepackage[left=1.5cm, right=1.5cm, top=1.785cm, bottom=2.0cm]{geometry}
\usepackage{balance}
\usepackage{mathptmx}
\usepackage{sectsty}
\usepackage{graphicx} 
\usepackage{lastpage}
\usepackage[format=plain,justification=justified,singlelinecheck=false,font={stretch=1.125,small,sf},labelfont=bf,labelsep=space]{caption}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{fnpos}
\usepackage[english]{babel}
\addto{\captionsenglish}{%
  \renewcommand{\refname}{Notes and references}
}
\usepackage{array}
\usepackage{droidsans}
\usepackage{charter}
\usepackage[T1]{fontenc}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{setspace}
\usepackage[compact]{titlesec}
\usepackage{hyperref}
%%%Please don't disable any packages in the preamble, as this may cause the template to display incorrectly.%%%

@@

\usepackage{subcaption}
\usepackage{nicefrac} % Include for inline fractions
\usepackage{url}

% \usepackage{cite}
\usepackage{xargs}
% Use more than one optional parameter in a new commands
\usepackage{color}
%
\usepackage[colorinlistoftodos,prependcaption,textsize=normalsize]{todonotes}
\usepackage{mdframed}

@@

\pagestyle{fancy}
\thispagestyle{plain}
\fancypagestyle{plain}{

%%%HEADER%%%
% \fancyhead[C]{\includegraphics[width=18.5cm]{head_foot/header_bar}}
% \fancyhead[L]{\hspace{0cm}\vspace{1.5cm}\includegraphics[height=30pt]{head_foot/journal_name}}
% \fancyhead[R]{\hspace{0cm}\vspace{1.7cm}\includegraphics[height=55pt]{head_foot/RSC_LOGO_CMYK}}
\renewcommand{\headrulewidth}{0pt}
}
%%%END OF HEADER%%%

%%%PAGE SETUP - Please do not change any commands within this section%%%
\makeFNbottom
\makeatletter
\renewcommand\LARGE{\@setfontsize\LARGE{15pt}{17}}
\renewcommand\Large{\@setfontsize\Large{12pt}{14}}
\renewcommand\large{\@setfontsize\large{10pt}{12}}
\renewcommand\footnotesize{\@setfontsize\footnotesize{7pt}{10}}
\makeatother

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand\footnoterule{\vspace*{1pt}% 
\color{cream}\hrule width 3.5in height 0.4pt \color{black}\vspace*{5pt}} 
\setcounter{secnumdepth}{5}

\makeatletter 
\renewcommand\@biblabel[1]{#1}            
\renewcommand\@makefntext[1]% 
{\noindent\makebox[0pt][r]{\@thefnmark\,}#1}
\makeatother 
\renewcommand{\figurename}{\small{Fig.}~}
\sectionfont{\sffamily\Large}
\subsectionfont{\normalsize}
\subsubsectionfont{\bf}
\setstretch{1.125} %In particular, please do not alter this line.
\setlength{\skip\footins}{0.8cm}
\setlength{\footnotesep}{0.25cm}
\setlength{\jot}{10pt}
\titlespacing*{\section}{0pt}{4pt}{4pt}
\titlespacing*{\subsection}{0pt}{15pt}{1pt}
%%%END OF PAGE SETUP%%%

%%%FOOTER%%%
\fancyfoot{}
\fancyfoot[LO,RE]{\vspace{-7.1pt}\includegraphics[height=9pt]{head_foot/LF}}
\fancyfoot[CO]{\vspace{-7.1pt}\hspace{13.2cm}\includegraphics{head_foot/RF}}
\fancyfoot[CE]{\vspace{-7.2pt}\hspace{-14.2cm}\includegraphics{head_foot/RF}}
\fancyfoot[RO]{\footnotesize{\sffamily{1--\pageref{LastPage} ~\textbar  \hspace{2pt}\thepage}}}
\fancyfoot[LE]{\footnotesize{\sffamily{\thepage~\textbar\hspace{3.45cm} 1--\pageref{LastPage}}}}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt} 
\renewcommand{\footrulewidth}{0pt}
\setlength{\arrayrulewidth}{1pt}
\setlength{\columnsep}{6.5mm}
\setlength\bibsep{1pt}
%%%END OF FOOTER%%%

%%%FIGURE SETUP - please do not change any commands within this section%%%
\makeatletter 
\newlength{\figrulesep} 
\setlength{\figrulesep}{0.5\textfloatsep}

\newcommand{\topfigrule}{\vspace*{-1pt}% 
\noindent{\color{cream}\rule[-\figrulesep]{\columnwidth}{1.5pt}} }

\newcommand{\botfigrule}{\vspace*{-2pt}% 
\noindent{\color{cream}\rule[\figrulesep]{\columnwidth}{1.5pt}} }

\newcommand{\dblfigrule}{\vspace*{-1pt}% 
\noindent{\color{cream}\rule[-\figrulesep]{\textwidth}{1.5pt}} }

\makeatother
%%%END OF FIGURE SETUP%%%

%%%TITLE, AUTHORS AND ABSTRACT%%%
\twocolumn[
  \begin{@twocolumnfalse}
{\includegraphics[height=30pt]{head_foot/journal_name}\hfill\raisebox{0pt}[0pt][0pt]{\includegraphics[height=55pt]{head_foot/RSC_LOGO_CMYK}}\\[1ex]
\includegraphics[width=18.5cm]{head_foot/header_bar}}\par
\vspace{1em}
\sffamily
\begin{tabular}{m{4.5cm} p{13.5cm} }

\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{An upper bound to gas storage and delivery via pressure-swing adsorption in
porous materials}} \\%Article title goes here instead of the text "This is the title"
\vspace{0.3cm} & \vspace{0.3cm} \\

 & \noindent\large{Jordan K. Pommerenck,$^{\ast}$\textit{$^{a}$} Cory M. Simon,\textit{$^{b}$} and David Roundy\textit{$^{a}$}} \\%Author names go here instead of "Full name", etc.

\includegraphics{head_foot/dates} & \noindent\normalsize{
Both hydrogen
and natural gas are challenging to economically store onboard vehicles as
fuels, due to their low volumetric energy density at ambient conditions.
One strategy to densify
these gases is to pack the fuel tank with a porous
adsorbent material.
% 
The US Department of
Energy (DOE) has set volumetric deliverable capacity
targets which, if met, would help
enable commercial adoption of hydrogen/natural gas as transportation fuels.
%
%Many have attempted to establish theoretical upper bounds on the deliverable
%capacity via pressure-swing adsorption using simplified models of the
%gas-substrate and gas-gas interaction~\cite{gomez2014exploring,
%gomez2017impact, kaija2018high, lee2019predicting}; none have established a
%rigorous upper bound on the deliverable capacity.
%
Here, we present a
theoretical upper bound on the deliverable capacity of a gas in a rigid
porous
material via an isothermal pressure swing.
%
To provide an extremum, we consider
a substrate that provides a spatially uniform potential energy field for the
gas. Our bound relies directly on experimentally measured
properties of the pure gas.
%
We conclude
that the deliverable capacity targets set by the DOE for room-temperature natural gas and hydrogen
storage are just barely theoretically possible.
The targets are likely to be impossible for any real,
rigid porous material because of steric
repulsion, which reduces the deliverable capacity below our upper
bound. Limitations
to the scope of applicability of our upper bound may guide fuel tank design and
future material development. Firstly, one could avoid using an \emph{isothermal}
pressure swing by heating the adsorbent to drive off
trapped, residual gas. Secondly,
our upper bound assumes the material does not change its
structure in response to adsorbed gas, suggesting that flexible materials could
still satisfy the DOE targets.}

%Any references in the abstract should be written out in full \textit{e.g.}\ [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].} \\%The abstrast goes here instead of the text "The abstract should be..."

\end{tabular}

 \end{@twocolumnfalse} \vspace{0.6cm}

  ]
%%%END OF TITLE, AUTHORS AND ABSTRACT%%%

%%%FONT SETUP - please do not change any commands within this section
\renewcommand*\rmdefault{bch}\normalfont\upshape
\rmfamily
\section*{}
\vspace{-1cm}

%%%FOOTNOTES%%%
\footnotetext{\textit{$^{*}$~E-mail: pommerjo@oregonstate.edu}}
\footnotetext{\textit{$^{a}$~Department of Physics, Oregon State University, Corvallis, OR 97331, USA.}}
\footnotetext{\textit{$^{b}$~School of Chemical, Biological, and Environmental Engineering, Oregon State University, Corvallis, OR 97331, USA. }}

%Please use \dag to cite the ESI in the main text of the article.
%If you article does not have ESI please remove the the \dag symbol from the title and the footnotetext below.

%\footnotetext{\dag~Electronic Supplementary Information (ESI) available: [details of any supplementary information available should be included here]. See DOI: 00.0000/00000000.}

%additional addresses can be cited as above using the lower-case letters, c, d, e... If all authors are from the same address, no letter is required

%\footnotetext{\ddag~Additional footnotes to the title and authors can be included \textit{e.g.}\ `Present address:' or `These authors contributed equally to this work' as above using the symbols: \ddag, \textsection, and \P. Please place the appropriate symbol next to the author's name and include a \texttt{\textbackslash footnotetext} entry in the the correct place in the list.}

%%%END OF FOOTNOTES%%%

%%%MAIN TEXT%%%%
\section{Introduction}
The transportation sector is dominantly powered by petroleum-based
fuels~\cite{davis2009transportation}. 
Consequently, in the United States, it is responsible
for 36\% of energy-related carbon dioxide emissions \cite{useia} and $\sim$50,000
premature deaths per year associated with particulate matter and ozone
emissions~\cite{caiazzo2013air}. 
Natural gas and hydrogen (H$_2$) are
alternative transportation fuels that, if adopted widely,
could mitigate climate change~\cite{mcglade2015geographical} and improve air quality for human
health. 
More, the finite global petroleum resources are declining
rapidly~\cite{sorrell2010global}.
The development of technologies for the
widespread adoption of sustainable transportation fuels, such as hydrogen, is therefore
critical.

@@

%%%END OF MAIN TEXT%%%

%The \balance command can be used to balance the columns on the final page if desired. It should be placed anywhere within the first column of the last page.

\balance

%If notes are included in your references you can change the title from 'References' to 'Notes and references' using the following command:
%\renewcommand\refname{Notes and references}

%%%REFERENCES%%%
\bibliography{bibfile} %You need to replace "rsc" on this line with the name of your .bib file
\bibliographystyle{rsc} %the RSC's .bst file

>>>>

\documentclass[pre,twocolumn]{revtex4-2}

\usepackage{graphicx} 
\usepackage{array}
\usepackage[usenames,dvipsnames]{xcolor}

@@

\usepackage{subcaption}
\usepackage{nicefrac} % Include for inline fractions
\usepackage{url}
\usepackage{amsmath}

% \usepackage{cite}
\usepackage{xargs}
% Use more than one optional parameter in a new commands
\usepackage{color}
%
\usepackage{mdframed}

@@

\author{Jordan Pommerenck}
\affiliation{Department of Physics, Oregon State University, Corvallis, OR 97331}
\author{Cory Simon}
\affiliation{Department of Chemical Engineering, Oregon State University, Corvallis, OR 97331}
\author{David Roundy}
\affiliation{Department of Physics, Oregon State University, Corvallis, OR 97331}

%  & \noindent\large{Jordan K. Pommerenck,$^{\ast}$\textit{$^{a}$} Cory M. Simon,\textit{$^{b}$} and David Roundy\textit{$^{a}$}} \\%Author names go here instead of "Full name", etc.
\begin{abstract}
    Both hydrogen
    and natural gas are challenging to economically store onboard vehicles as
    fuels, due to their low volumetric energy density at ambient conditions.
    One strategy to densify
    these gases is to pack the fuel tank with a porous
    adsorbent material.
    % 
    The US Department of
    Energy (DOE) has set volumetric deliverable capacity
    targets which, if met, would help
    enable commercial adoption of hydrogen/natural gas as transportation fuels.
    %
    %Many have attempted to establish theoretical upper bounds on the deliverable
    %capacity via pressure-swing adsorption using simplified models of the
    %gas-substrate and gas-gas interaction~\cite{gomez2014exploring,
    %gomez2017impact, kaija2018high, lee2019predicting}; none have established a
    %rigorous upper bound on the deliverable capacity.
    %
    Here, we present a
    theoretical upper bound on the deliverable capacity of a gas in a rigid
    porous
    material via an isothermal pressure swing.
    %
    To provide an extremum, we consider
    a substrate that provides a spatially uniform potential energy field for the
    gas. Our bound relies directly on experimentally measured
    properties of the pure gas.
    %
    We conclude
    that the deliverable capacity targets set by the DOE for room-temperature natural gas and hydrogen
    storage are just barely theoretically possible.
    The targets are likely to be impossible for any real,
    rigid porous material because of steric
    repulsion, which reduces the deliverable capacity below our upper
    bound. Limitations
    to the scope of applicability of our upper bound may guide fuel tank design and
    future material development. Firstly, one could avoid using an \emph{isothermal}
    pressure swing by heating the adsorbent to drive off
    trapped, residual gas. Secondly,
    our upper bound assumes the material does not change its
    structure in response to adsorbed gas, suggesting that flexible materials could
    still satisfy the DOE targets.    
\end{abstract}

\maketitle

%%%FOOTNOTES%%%
% \footnotetext{\textit{$^{*}$~E-mail: pommerjo@oregonstate.edu}}
% \footnotetext{\textit{$^{a}$~Department of Physics, Oregon State University, Corvallis, OR 97331, USA.}}
% \footnotetext{\textit{$^{b}$~School of Chemical, Biological, and Environmental Engineering, Oregon State University, Corvallis, OR 97331, USA. }}

\section{Introduction}
The transportation sector is dominantly powered by petroleum-based
fuels~\cite{davis2009transportation}. 
Consequently, in the United States, it is responsible
for 36\% of energy-related carbon dioxide emissions \cite{useia} and $\sim$50,000
premature deaths per year associated with particulate matter and ozone
emissions~\cite{caiazzo2013air}. 
Natural gas and hydrogen (H$_2$) are
alternative transportation fuels that, if adopted widely,
could mitigate climate change~\cite{mcglade2015geographical} and improve air quality for human
health. 
More, the finite global petroleum resources are declining
rapidly~\cite{sorrell2010global}.
The development of technologies for the
widespread adoption of sustainable transportation fuels, such as hydrogen, is therefore
critical.

@@

%%%REFERENCES%%%
\bibliography{bibfile} %You need to replace "rsc" on this line with the name of your .bib file
